Automated Synthesis of State-Space Digital Systems

### 2016-12-20 cav2017/cav2017.tex
typos

Careful examination of these matrices reveals that because the $\mat{A}_t$ is upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$ which can be calculated separately. Additionally, these correspond to the roots of the polynomials
\begin{align*}
\left(z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}\right) \left(z^n+\sum_{i=1}^p{(p_i-a_i)z^{n-i}}\right)
\end{align*}

For a stabilised closed loop, we need these roots to remain within the unit circle (left hand side of the plane for continuous time).
Whilst this is not a sufficient condition for verifying safety properties, it is a necessary one, therefore we will review this verification process.
The direct approach would be to calculate the roots of the polynomials (\emph{ie} the eigenvalues of the matrix), but this ends up being to costly, particularly in the case of synthesis, so we use an indirect method.

>>>>

Careful examination of these matrices reveals that because the $\mat{A}_t$ is upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$ which can be calculated separately. Additionally, these correspond to the roots of the following polynomials:
\begin{align*}
\left(z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}\right) \left(z^n+\sum_{i=1}^p{(p_i-a_i)z^{n-i}}\right)
\end{align*}

For a stabilised closed loop, we need these roots to remain within the
unit circle (left hand side of the plane for continuous time).  Whilst
this is not a sufficient condition for verifying safety properties, it
is a necessary one, therefore we will review this verification
process.  The direct approach would be to calculate the roots of the
polynomials (\emph{ie} the eigenvalues of the matrix), but this ends
up being too costly, particularly in the case of synthesis, so we use
an indirect method.
